$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2013-10-07 JournalToSubmit2013/1-intro.tex
intro --mam

\section{SOD-M}\label{sec:sodm}
The Service-Oriented Development Method (SOD-M)~\cite{decastro1} is a MDD approach for service-based applications.
SOD-M provides a framework with models and standards to express functionalities of applications at a high-level of abstraction. 
SOD-M meta-models are organized into three levels: CIM (\textit{Computational Independent Models}), PIM (\textit{Platform Independent Models}) and PSM (\textit{Platform Specific Models}).

Two models are defined at the CIM level: \textit{value model} 
and \textit{BPMN model}. 
The PIM level models the entire structure of the application flow,
while, the PSM level provides transformations towards more specific platforms.
The PIM-level models are: \textit{use case}, \textit{extended use case}, \textit{service process} and
\textit{service composition}. The PSM level models are: \textit{web service interface}, \textit{extended composition service} and \textit{business logic}. 
These three levels have no support for describing non-functional requirements.

>>>>

\section{SOD-M}\label{sec:sodm}
The Service-Oriented Development Method (SOD-M)~\cite{decastro1} is a MDD approach for service-based applications.
SOD-M provides models and notation to specify service applications at different levels of abstraction. 
As usual for MDD, SOD-M meta-models are organized into three levels: CIM (\textit{Computational Independent Models}), PIM (\textit{Platform Independent Models}) and PSM (\textit{Platform Specific Models}).

Two models are defined at the CIM level: \textit{value model} 
and \textit{BPMN model}. 
\textsc{Explain these two here --Martin.}

Models at the PIM level describe the structure of the application flow,
while, the PSM level provides transformations towards more specific platforms.
The PIM-level models proposed by SOD-M are: 
\begin{trivlist}
\item \textit{use case}: 
\item \textit{extended use case}:
\item \textit{service process}:
\item \textit{service composition}. 
\end{trivlist}

SOD-M defines three meta-models at the PSM level: \textit{web service interface}, \textit{extended composition service} and \textit{business logic}. 
These three levels have no support for describing non-functional requirements.
